### 2019-06-04 doc/chapters/trying_verify_checktx.tex
fixed
fixed order

This chapter describes some parts of Bitcoin-S.
We are going to create a transaction and show you the relevant parts of checkTransaction, where transactions are checked against some properties.
Then we see some troubles occurred during this work.
In the end you will see how we fixed a bug in Bitcoin-S.

@@

The relevant part for the property we are trying to verify is the following.
\begin{lstlisting}[language=scala]
  val prevOutputTxIds = transaction.inputs.map(_.previousOutput.txId)
  val noDuplicateInputs = prevOutputTxIds.distinct.size == prevOutputTxIds.size
\end{lstlisting}

@@

There is a bug, because checkTransaction checks on the transaction id that we are going to explain a next section.

But before that you can read about the bug we found and fixed in the next section.

>>>>

This chapter describes some parts of Bitcoin-S needed to verify our property.
We are going to create a transaction and show you the relevant parts of checkTransaction, where transactions are checked against some properties.
Then we see some troubles occurred during this work.
In the end you will see how we fixed a bug in Bitcoin-S.

@@

The relevant part for the bug we found.
\begin{lstlisting}[language=scala]
  val prevOutputTxIds = transaction.inputs.map(_.previousOutput.txId)
  val noDuplicateInputs = prevOutputTxIds.distinct.size == prevOutputTxIds.size
\end{lstlisting}

@@

There is a bug, because checkTransaction checks on the transaction id that we are going to explain the next section.
